### 2021-03-12 README.Rmd
get_ids bugfix

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
taxadb:::td_disconnect()
```

@@

To get started, install the development version directly from GitHub:

```{r eval=FALSE}
devtools::install_github("ropensci/taxadb")
```

@@

```{r }
td_create("col")
```

@@

```{r}
birds <- bbs %>% 
  select(species) %>% 
  mutate(id = get_ids(species, "col"))

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  comment = "#>"
)
taxadb:::td_disconnect()
```

@@

To get started, install from CRAN

``` r
install.pacakges("taxadb")
```

or install the development version directly from GitHub:

``` r
devtools::install_github("ropensci/taxadb")
```

@@

```{r }
td_create("col", overwrite=FALSE)
```

@@

```{r}
birds <- bbs %>% 
  select(species) %>% 
  mutate(id = taxalight::get_ids(species, "col"))
